A Comparison of Graph Processing Systems

### 2020-09-25 documentation/paper/main.tex

@@

\begin{document}

@@

>>>>

\usepackage[
  title={A Comparison of Graph Processing Systems},
  author={Simon König (3344789)\\Leon Matzner (3315161)\\Felix Rollbühler (3310069)\\Jakob Schmid (3341630)\\},
  type={Bachelor-Forschungsprojekt},
  institute=ipvs,
  course={Informatik},
  examiner={Prof.\ Dr.\ rer.\ nat.\ Kurt Rothermel},
  supervisor={Heiko Geppert,\ M.Sc.},
  startdate={April 1, 2020},
  enddate={October 1, 2020},
  language=english
]{scientific-thesis-cover}

@@

\begin{document}
\Coverpage

@@

\Affirmation
